---
title: 'ISE537 Homework #2'
author: "Keenan Smith"
date: "3/2/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1) Prediction is the only objective of multiple linear regression. 
☐ True ☐ False
2) In multiple linear regression, we study the relationship between a single response variable and several predicting quantitative and/or qualitative variables.
☐ True ☐ False
3) A multiple linear regression model contains 5 quantitative predicting variables and an intercept. The number of parameters to estimate is 6. 
☐ True ☐ False
4) Given a qualitative predicting variable with 7 categories in a linear regression model with intercept, 7 dummy variables need to be included in the model. 
☐ True ☐ False
5) In multiple linear regression, quantitative variables can be transformed into qualitative or categorical variables. 
☐ True ☐ False
6) The estimated variance of the error terms of a multiple linear regression model with intercept can be obtained by summing up the squared residuals and dividing that by n – p, where n is the sample size and p is the number of predictors. 
☐ True ☐ False
7) In a first-order multiple linear regression model, the estimated regression coefficient corresponding to a quantitative predicting variable is interpreted as the estimated expected change in the response variable when there is a change of one unit in the corresponding predicting variable holding all other predictors fixed. 
☐ True ☐ False
8) In multiple linear regression, the estimation of the variance of the error terms is unnecessary for making statistical inference on the regression coefficients. 
☐ True ☐ False
9) In multiple linear regression, the sampling distribution used for estimating confidence intervals for the regression coefficients is the normal distribution. 
☐ True ☐ False
10) The estimated regression coefficients obtained by using the method of least squares are biased estimators of the true regression coefficients. 
☐ True ☐ False
11) Conducting t-tests on each parameter 𝛽 is preferable to an F-test when testing the overall significance of a multiple linear regression model. 
☐ True ☐ False
12) A partial F-test can be used to test the null hypothesis that the regression coefficients associated with a subset of the predicting variables in a multiple linear regression model are all equal to zero. 
☐ True ☐ False
13) In multiple linear regression, if the F-test statistic is greater than the appropriate F-critical value, then at least one of the slope coefficients is significantly different from zero at the given significance level. 
☐ True ☐ False
14) In multiple linear regression, the uncertainty of the prediction of a new response comes only from the newness of the observation. 
☐ True ☐ False


Library Import
```{r}
library(tidymodels)
library(tidyverse)
tidymodels_prefer()
```


Import Dataset and Tidy
```{r cars}
fish <- read_csv("fish.csv")
fram <- read_csv("fram.csv")

fish <-
  fish %>%
  rename(weight = Weight,
         species = Species,
         body_heigh = `Body Height`,
         total_length = `Total Length`,
         diagonal_length = `Diagonal Length`,
         height = Height,
         width = Width)
fram <-
  fram %>%
  rename(sex = SEX,
         age = AGE,
         sysbp = SYSBP,
         cursmoke = CURSMOKE,
         bmi = BMI) %>%
  mutate(sex_fact = as.factor(sex),
         cursmoke_fact = as.factor(cursmoke))

fram_mod <-
  fram %>%

  filter(bmi >= 30)

fram

```

```{r}
# Creating Linear Regression Model Engine
lm_model <-
  linear_reg() %>%
  set_engine("lm")
```

```{r}

#Spending Data Allocation for Modelling
# set.seed(123)
# ames_split <- initial_split(ames, prop = 0.80, strata = Sale_Price)
# ames_train <- training(ames_split)
# ames_test <- testing(ames_split)

#Recipe Creation for Tidy Models
fram_rec <-
  recipe(sysbp ~ sex_fact + cursmoke_fact + bmi, data = fram) %>%
  step_dummy(all_nominal_predictors())

summary(fram_rec)
# Creating Workflow for Tidy Models
lm_wflow <-
  workflow() %>%
  add_recipe(fram_rec) %>%
  add_model(lm_model)
  
# Fitting the Linear Regression to the Data
lm_fit <- fit(lm_wflow, fram)

# Tidying the Fitted Data
lm_fit %>%
  extract_fit_parsnip() %>%
  tidy()

# Bringing the Model back into Base R to use Base R functions on the Model
lm_fit_var <- lm_fit %>% extract_fit_engine()

fram_residuals <- tibble(residuals = lm_fit_var$residuals)
summary(lm_fit_var)
plot(lm_fit_var)
```

```{r}
#Recipe Creation for Tidy Models
modified_rec <-
  recipe(sysbp ~ sex + cursmoke + bmi, data = fram_mod) %>%
  step_dummy(all_nominal_predictors())

# Creating Workflow for Tidy Models
lm_wflow_fram_mod <-
  workflow() %>%
  add_recipe(modified_rec) %>%
  add_model(lm_model)
  
# Fitting the Linear Regression to the Data
lm_fit_mod <- fit(lm_wflow_fram_mod, fram_mod)

# Tidying the Fitted Data
lm_fit_mod %>%
  extract_fit_parsnip() %>%
  tidy()

# Bringing the Model back into Base R to use Base R functions on the Model
lm_fit_var_mod <- lm_fit_mod %>% extract_fit_engine()

summary(lm_fit_var_mod)
plot(lm_fit_var_mod)
```

